<!-- First level headers create new appendix section and a label "Appendix N" -->
<!-- Appendix structure: -->
<!-- A: Behavioral analysis -->
<!-- A0: trial criteria location-approach -->
<!-- A1: Location descriptives -->
<!-- - plot rt / acc, table -->
<!-- A2: robust descriptives -->
<!-- - plot rt /acc, table -->
<!-- A3: classic descriptives -->
<!-- -plot rt / acc, table -->

<!-- B: Model comparion -->

<!-- c: Results classical PES account -->

<!-- D: Hierarchical Model -->

# Behavioral analysis
## Classification of Go trials
### Robust Approach
### Location Approach
### Classical Approach

## Descriptive results 
### Robust
### Location
### Classical

# Model comparison
## Model specifications
## LOO
```{r appendix-rsi-compare}
rsi_comp %>% 
  as.data.frame() %>% 
  mutate(model = rownames(.)) %>% 
  select(model, elpd_loo, elpd_diff, se_diff) %>% 
  remove_rownames() %>% 
  apa_table(caption = "Model comparison",
            note = "The base model allows all parameters to be influenced by both factors RSI and error-condition. The 'no_rsi_model' allows none of the parameters to be influenced by RSI. The other four models only all other parameters but the parameter listed in the name to vary between RSI")
```

```{r appendix-err-compare}
err_comp %>% 
  as.data.frame() %>% 
  mutate(model = rownames(.)) %>% 
  select(model, elpd_loo, elpd_diff, se_diff) %>% 
  remove_rownames() %>% 
  apa_table(caption = "Model comparison",
            note = "The base model allows all parameters to be influenced by both factors RSI and error-condition. The 'no_error_factor_model' allows none of the parameters to be influenced by error-condition. The other four models only all other parameters but the parameter listed in the name to vary between error-conditions")
```

```{r appendix-only-compare}
only_comp %>% 
  as.data.frame() %>% 
  mutate(model = rownames(.)) %>% 
  select(model, elpd_loo, elpd_diff, se_diff) %>% 
  remove_rownames() %>% 
  apa_table(caption = "Model comparison",
            note = "The base model allows all parameters to be influenced by both factors RSI and error-condition. The 'no_error_factor_model' allows none of the parameters to be influenced by error-condition. The other four models only allow the parameter listed in the name to vary between error-conditions")
```

# Full Location Model
## Model results
```{r appendix-drift-rsi-plot, fig.cap = 'Drift rate depending on location and RSI. The gray bar represents the occurence of a NoGo trial. Error bars represent 95% CrI.'}
drift_location_rsi_plot
```

```{r appendix-bs-rsi-plot, fig.cap = 'Boundary separation depending on location and RSI. The gray bar represents the occurence of a NoGo trial. Error bars represent 95% CrI.'}
bs_location_rsi_plot
```

```{r appedix-ndt-rsi-plot, fig.cap = 'Non-decision time depending on location and RSI. The gray bar represents the occurence of a NoGo trial. Error bars represent 95% CrI.'}
ndt_location_rsi_plot
```

```{r appendix-bias-rsi-plot, fig.cap = 'Bias towards the previously not shown response depending on location and RSI. The gray bar represents the occurence of a NoGo trial. Error bars represent 95% CrI.'}
bias_location_rsi_plot
```

# Classic PES results
## Diffusion model fit
## Diffusion model results

# Hierarchical model
## Model specification
## Model fit
## Model results

```{r appendix-table-location-counts, results = 'asis'}
count_table <- diffusion_data_location %>% count(rsi, location)

apa_table(count_table, caption = "Number of trials per condition")
```
```{r appendix-mean-values-power-analysis, results = 'asis', eval = FALSE}
# estimated_mean_values_table 
# commented out because no power analysis reported anymore
```