# Results
```{r results-source-descriptive-analysis, child = "markdown/descriptive_analysis.Rmd"}
```

```{r results-source-significance-testing, child = "markdown/significance_testing.rmd"}
```
## Behavioral Analysis
All analysis was conducted using `r r_citations$r`. `r r_citations$pkgs`
After data cleaning, `r nrow(final_data)` trials from `r demo_output$n_subjects - n_outliers` participants remained. Participants falsely responded in `r descriptive_output$mean_error_rate_nogo`% of NoGo trials resulting in a median `r average_n_nogo_error %>% filter(classic_pes_type == "post_error") %>% pull(median)` (SD = `r average_n_nogo_error %>% filter(classic_pes_type == "post_error") %>% pull(sd)`) post-error trials and `r average_n_nogo_error %>% filter(classic_pes_type == "post_correct") %>% pull(median)` (SD = `r average_n_nogo_error %>% filter(classic_pes_type == "post_correct") %>% pull(sd)`) post-correct trials per participant. Descriptive statistics can be found in Table \@ref(tab:results-descriptive-analysis-overview-table).

```{r results-descriptive-analysis-overview-table, results = 'asis'}
descriptive_analysis_overview_table %>% 
  apa_table(., caption = "Mean response times (RT), mean accuracies (ACC) by condition", note = "SDs in parentheses. RSI = response stimulus interval. Previous accuracy denotes C+1 if the previous trial was a correct NoGo trial and E+1 if there was an erroneous response to the previous NoGo trial, NA is printed if the previous trial was a Go trial.")
```

Highly significant main effects of RSI, `r apa_print(aov_rt_rsi_error_classic, es = "pes", mse = FALSE)$full_result$rsi` and accuracy of previous trial, `r apa_print(aov_rt_rsi_error_classic, es = "pes", mse = FALSE)$full_result$classic_pes_type` on reaction time were observed. Critically, the interaction between RSI and previous accuracy was highly significant, `r apa_print(aov_rt_rsi_error_classic, es = "pes", mse = FALSE)$full_result$rsi_classic_pes_type`. Post-hoc comparison reveals an increased influence of previous accuracy in the short RSI condition, manifesting in an increase in PES.

Comparison of mean accuracy between the 2x2 conditions yielded similar patterns of significant main effects of RSI `r apa_print(aov_acc_rsi_error_classic, es = "pes", mse = FALSE)$full_result$rsi` and previous accuracy `r apa_print(aov_acc_rsi_error_classic, es = "pes", mse = FALSE)$full_result$classic_pes_type` and a significant interaction effect, `r apa_print(aov_acc_rsi_error_classic, es = "pes", mse = FALSE)$full_result$rsi_classic_pes_type`. Errors commited in the short RSI condition lead to a more significant decrease in accuracy on the trial immediately following the error.

```{r results-anova-rsi-rt, results = 'asis', eval = FALSE}
# Maybe move these to appendix
apa_print(aov_rt_rsi_error_classic)$table %>% 
  mutate(
    term = c("RSI", "previous accuracy", "RSI $\\times$ previous accuracy")
  ) %>% 
  rename(
    "Effect" = term
  ) %>% 
  apa_table(
    caption = "Effects of RSI and previous accuracy on mean reaction times",
    note = "Both factors were manipulated within participants, with RSI being either 200ms or 1000ms. Previous accuracy refers to the accuracy of the response in the previous NoGo trial")
```

```{r results-anova-rsi-acc, results = 'asis', eval = FALSE}
apa_print(aov_acc_rsi_error_classic)$table %>% 
  mutate(
    term = c("RSI", "previous accuracy", "RSI $\\times$ previous accuracy")
  ) %>% 
  rename(
    "Effect" = term
  ) %>% 
  apa_table(
    caption = "Effects of RSI and previous accuracy on mean accuracy",
    note = "Both factors were manipulated within participants, with RSI being either 200ms or 1000ms. Previous accuracy refers to the accuracy of the response in the previous NoGo trial")
```

## Diffusion Model
