# Results
```{r results-source-descriptive-analysis, child = "markdown/descriptive_analysis.Rmd"}
```

```{r results-source-significance-testing, child = "markdown/significance_testing.rmd"}
```
All analysis was conducted using the `r r_citations` software. After data cleaning, `r nrow(final_data)` trials from `r demo_output$n_subjects - n_outliers` participants remained. Participants falsely responded in `r descriptive_output$mean_error_rate_nogo`% of NoGo trials resulting in a median `r average_n_nogo_error %>% filter(classic_pes_type == "post_error") %>% pull(median)` post-error trials (SD = `r average_n_nogo_error %>% filter(classic_pes_type == "post_error") %>% pull(sd)`) and `r average_n_nogo_error %>% filter(classic_pes_type == "post_correct") %>% pull(median)` (SD = `r average_n_nogo_error %>% filter(classic_pes_type == "post_correct") %>% pull(sd)`) post-correct trials. Descriptive statistics can be found in Table \@ref(tab:results-descriptive-analysis-overview-table).

```{r results-descriptive-analysis-overview-table, results = 'asis'}
descriptive_analysis_overview_table
```

Highly significant main effects of RSI, `r apa_print(aov_rt_rsi_error_classic, es = "pes", mse = FALSE)$full_result$rsi` and accuracy of previous trial, `r apa_print(aov_rt_rsi_error_classic, es = "pes", mse = FALSE)$full_result$classic_pes_type` on reaction time were observed. Critically, the interaction between RSI and previous accuracy was highly significant, `r apa_print(aov_rt_rsi_error_classic, es = "pes", mse = FALSE)$full_result$rsi_classic_pes_type` **(see Table \@ref(tab:results-anova-rsi-rt))**. Post-hoc comparison reveals an increased influence of previous accuracy in the short RSI condition, manifesting in an increase in PES. **Estimated marginal means obtained post-hoc can be found in Table \@ref(tab:results-emmeans-rsi-rt) in the appendix.**

Comparison of mean accuracy within participants between the 2x2 conditions yielded similar patterns of significant main effects of RSI and previous accuracy and a significant interaction effect, `r apa_print(aov_acc_rsi_error_classic, es = "pes", mse = FALSE)$full_result$rsi_classic_pes_type` **(see Table \@ref(tab:results-anova-rsi-acc))**. Participants accuracy shrank more intensely after an error committed in the short RSI-condition. **Estimated marginal means obtained post-hoc can be found in Table \@ref(tab:results-emmeans-rsi-acc) in the appendix.**

```{r results-anova-rsi-rt, results = 'asis', eval = FALSE}
# Maybe move these to appendix
apa_print(aov_rt_rsi_error_classic)$table %>% 
  mutate(
    term = c("RSI", "previous accuracy", "RSI $\\times$ previous accuracy")
  ) %>% 
  rename(
    "Effect" = term
  ) %>% 
  apa_table(
    caption = "Effects of RSI and previous accuracy on mean reaction times",
    note = "Both factors were manipulated within participants, with RSI being either 200ms or 1000ms. Previous accuracy refers to the accuracy of the response in the previous NoGo trial")
```

```{r results-anova-rsi-acc, results = 'asis', eval = FALSE}
apa_print(aov_acc_rsi_error_classic)$table %>% 
  mutate(
    term = c("RSI", "previous accuracy", "RSI $\\times$ previous accuracy")
  ) %>% 
  rename(
    "Effect" = term
  ) %>% 
  apa_table(
    caption = "Effects of RSI and previous accuracy on mean accuracy",
    note = "Both factors were manipulated within participants, with RSI being either 200ms or 1000ms. Previous accuracy refers to the accuracy of the response in the previous NoGo trial")
```


## Outline Results
- data included
- outliers and data excluded
- behavioral description of effects
- replicate pes, check interaction RSI and so forth
- diffusion modelling things
- describe differential effects of errors on parameters in RSI conditions

