# Results
```{r library calls}
library(tidyverse)
```

```{r imports}
descriptive_output <- rio::import("./markdown/data/descriptive_output.rdata")
# load("./data/aov_rt_rsi_error_classic.rdata")
# load("./data/aov_acc_rsi_error_classic.rdata")
```

```{r child = "markdown/significance_testing.rmd"}
```

We found significant effects of rsi `r apa_print(aov_rt_rsi_error_classic)$statistic$rsi`, significant effects of error type `r apa_print(aov_rt_rsi_error_classic)$statistic$classic_pes_type` and crucially a significant interaction effect `r apa_print(aov_rt_rsi_error_classic)$statistic$rsi_classic_pes_type`.

Full result: `r apa_print(aov_rt_rsi_error_classic)$full_result$rsi_classic_pes_type`.

A table can be found here
`r apa_table(apa_print(aov_rt_rsi_error_classic)$table, caption = "Anova Results")`


## Outline Results
- data included
- outliers and data excluded
- behavioral description of effects
- replicate pes, check interaction RSI and so forth
- diffusion modelling things
- describe differential effects of errors on parameters in RSI conditions

## Trying data insertation
```{r data table, echo = FALSE}
data <- tibble(first = 1:5, second = 1:5, third = 1:5, fourth = 1:5)
```

```{r display, results = "asis"}
knitr::kable(data, caption = "some data")
```

