---
editor_options:
  chunk_output_type: console
---

```{r setup}
library(Superpower)
```

# Power Analysis
Checking if planned design has enough power. Means and sd of drift rates and boundary separations was extracted from @dutilh2012testing and @dutilh2013.
They only "reported" se of values. Sd was calculated from this using the formula
$sd = se * sqrt(n)$

Values had to be estimated from plots in those studies, both have long RSI

Mean values from @dutihl2013 (young participants)
drift rate (mean, sd): 
pre: 0.23, 0.05
post: 0.18, 0.05

boundary sep (mean, sd):
pre: 0.125, 0.025
post: 0.157, 0.025

values from @dutilh2012testing
drift rate (word freq2):
pre: 0.23, 0.06
post: 0.23, 0.06

boundary sep (mean, sd):
pre: 0.133, 0.018
post: 0.148, 0.018

@schroder2020 shows high intercorrelation between pre- and post-error RT (>0.7). But ddm paramters often contain more unsystematic error variance due to the estimation process @lerche2017. @yap2012 do however find good within-session reliabilities of ddm paramters **reliability even good estimator here, since we are measuring different parameter conditions?**. @lerche2017 also report test-retest reliabilites in ranges from 0.6-0.8 for most experiments and estimation procedures on drift rate and boundary separation.

Mean values generated using these assumptions:
Drift rate in short RSI slightly lower than in long RSI **(look up effect of RSI on drift rate)** 
drift rate takes larger decrease in short rsi following an error, post driftrate (short) was estimated from dutilh2012testing because they only ones to show decrease

boundary sep same assumptions, but now interaction effect leading to higher increases in boundary sep following an error in long rsi. Values for short RSI PE were guessed


```{r setting up power}
my_design <- "2w*2w" # 2 within factors (pre- vs. post-error; short/long rsi)

alpha <- 0.05 # alpha level of tests

my_n <- 50 # initial guess, becomes irrelevant with power curves

mu_drift <- c(# mean values of drift rate in the 2x2 conditions
  0.23,
  0.24,
  0.18,
  0.22
)

sd_drift <- 0.08 # sd of drift rate

mu_boundary <- c(# mean values of boundary sep in the 2x2 conditions
  0.12,
  0.13,
  0.135,
  0.155
)

sd_boundary <- 0.02
  
my_r <- 0.7 # correlation between values (can be specified for each bivariate correlation separately)

my_labelnames <- c(
  "type", "e-1", "e+1",
  "rsi", "short", "long"
  ) # names of factors
```

```{r design drift}
design_result_drift <- ANOVA_design(
  design = my_design,
  n = my_n,
  mu = mu_drift,
  sd = sd_drift,
  r = my_r,
  labelnames = my_labelnames
)

```

```{r exact drift}
exact_result_drift <- ANOVA_exact(design_result_drift,
                            alpha_level = alpha,
                            verbose = FALSE)
```

```{r power plot drift}
power_drift <- plot_power(
  design_result_drift,
  min_n = 50,
  max_n = 100,
  desired_power = 80,
  plot = TRUE,
  verbose = TRUE
  )
```

```{r design boundary}
design_result_boundary <- ANOVA_design(
  design = my_design,
  n = my_n,
  mu = mu_boundary,
  sd = sd_boundary,
  r = my_r,
  labelnames = my_labelnames
)

```

```{r exact boundary}
exact_result_boundary <- ANOVA_exact(design_result_boundary,
                            alpha_level = alpha,
                            verbose = FALSE)
```

```{r power plot boundary}
power_boundary <- plot_power(
  design_result_boundary,
  min_n = 50,
  max_n = 100,
  desired_power = 80,
  plot = TRUE
)
```

